My Cool Title

### 2019-04-30 paper.tex
Added unguided experiment section and section on environment design

\usepackage{graphicx}

@@

@@

>>>>

\usepackage{graphicx}
\usepackage{booktabs}

@@

The design goal of this experiment is to mimic how a typical person with healthy eyesight would behave if told to look for a given object. 
In such a scenario, a person would exploit the objects currently within their view and their prior knowledge on a room's typical layout to make a decision on where to look next to find what they are looking for. 
Take for example a person in bathroom facing the basin after washing their hands and looking for a hand-dryer. 
It is unlikely that a hand dryer would be placed above or below a wash basin so it it is reasonable to believe that they would instinctively look at chest height on the walls to their left, right or behind them to find a dryer.

For this experiment, a mobile camera and object detector acts as the participant's eyes and informs them what the objects within the camera's view and it is then up to the participant to exploit their prior knowledge of the given environment in order to manipulate the camera to point towards the target object. 
The object detector was implemented in an Android app that uses the object classifier and Android's Text-to-Speech engine to read out any objects that it detected. 
The app only reads out the objects when the participant requested it to by tapping on the screen. 
When the target object comes within the camera's view and is correctly classified by the object detector, the device vibrated to inform the participant.

Each participant was verbally told what the target object was they they were meant to find and each participant was given 45 seconds to find the target object. 
In this case, the learning effect was ignored in order to mimic the typical search behaviour described earlier. 
Each experiment run was ended when a target was found or the time limit was reached. 
This process was repeated a total of 8 times, once for each target object within the environment.

@@

\subsection{Environment Setup}

The environment, and the object placement within it, for both experiments was modelled on a typical office.
Measures were taken to ensure that both office environments were unique in layout and object placement. 
However, for the larger, more static objects (e.g.\ a desk or door) there is cross-experiment occurrences, since most offices contain the same basic furniture and objects. 
These objects were placed in different locations relative to each other for the 2 experiments to minimise any learning effects that may occur between the experiments. 
All of the objects and their experiment placement is given in Table~\ref{tab:objects}.

\begin{table}
  \centering
  \caption{The different objects used within each experiment environment.}\label{tab:objects}
  \begin{tabular}{p{2cm}cp{0.7cm}c}
    \toprule
    & \bf{Guided} & & \bf{Unguided} \\\midrule
    Door        & X & & X \\\midrule
    Desk	& X & & X \\\midrule
    Chair	& X & & X \\\midrule
    Whiteboard	& X & & X \\\midrule
    Mouse	& X & & X \\\midrule
    Monitor	&   & & X \\\midrule
    Telephone	&   & & X \\\midrule
    Keyboard	&   & & X \\\midrule
    Laptop	& X & &   \\\midrule
    Backpack	& X & &   \\\midrule
    Mug		& X & &   \\\midrule
    \bottomrule
  \end{tabular}
\end{table}
